Guarded Recursive Type Theory via Sized Types

### 2019-01-10 code-oneclock-paper/latex/paper.tex
All the code

\usepackage{newunicodechar}

@@

\newunicodechar{⊤}{$\top$}
\newunicodechar{≡}{$\equiv$}
\newunicodechar{₁}{$_1$}
\newunicodechar{Γ}{$\Gamma$}
\newunicodechar{Σ}{$\Sigma$}
\newunicodechar{λ}{$\lambda$}
\newunicodechar{∙}{$\cdot$}

% Add more as you need them (shouldn't happen often).

@@

% New commands for Agda inline code
\newcommand{\D}{\AgdaDatatype}
\newcommand{\IC}{\AgdaInductiveConstructor}
\newcommand{\F}{\AgdaFunction}
\newcommand{\Ar}{\AgdaArgument}
\newcommand{\Fi}{\AgdaField}

@@

\section{Preliminaries}
%% \input{Prelude/Basics}
%% \input{Presheaves/Presheaves}
%% \input{Presheaves/Const}
%% \input{Presheaves/Terminal}
%% \input{Presheaves/Product}
%% \input{Presheaves/Sum}
%% \input{Presheaves/Exp}
%% \input{CloTT/Structure/Contexts}
%% \input{CloTT/Structure/Types}
%% \input{CloTT/Structure/Terms}
%% \input{CloTT/Structure/DefinitionalEquality}
%% \input{CloTT/Structure/ContextOperations}
%% \input{CloTT/Structure/Subst}
%% \input{CloTT/TypeFormers/UnitType}
%% \input{CloTT/TypeFormers/SumType}
%% \input{CloTT/TypeFormers/ProductType}
%% \input{CloTT/TypeFormers/FunctionType}
%% \input{CloTT/TypeFormers/ClockQuantification}
%% \input{CloTT/TypeFormers/Later}
%% \input{CloTT/TypeFormers/LaterType}
%% \input{CloTT/TypeFormers/WeakenClock}
%% \input{CloTT/TypeFormers/Fix}
%% \input{CloTT/TypeFormers/Force}

@@

\subsection{Guarded Recursive Type Theory}

\section{Presheaves}
A presheaf is a functor from the category of sizes to \D{Set}.

\input{Presheaves/Presheaves}

Every type \Ar{A} in \D{Set} defines a constant presheaf whose action
on \Ar{i} is given by \Ar{A}, for any size \Ar{i}.
\input{Presheaves/Const}

Presheaves are the objects of a category whose morphisms are natural
transformations. This is a cartesian closed category with finite
coproducts.
The terminal object is the constant presheaf on the unit type \D{⊤},
i.e. \D{Terminal} = \D{Const ⊤}. Given two presheaves \Ar{P} and
\Ar{Q}, we write \D{Prod} \Ar{P} \Ar{Q} for their cartesian
product. The action of \D{Prod} \Ar{P} \Ar{Q} on a size \Ar{i} is
defined as follows:
\remove{
\input{Presheaves/Product}
%\Fi{PSh.Obj} \Ar{P i ×} \Fi{PSh.Obj} \Ar{Q i}.
Coproducts are also defined in a similar pointwise way.

Given two presheaves \Ar{P} and
\Ar{Q}, we write \D{Exp} \Ar{P} \Ar{Q} for their exponential. 
 The action of \D{Exp} \Ar{P} \Ar{Q} on a size \Ar{i} is
defined as follows:
\input{Presheaves/Exp}
}
\section{The Model}

\subsection{Types, Contexts, Terms}
A context in \IC{set} is an element of \D{Set}. A context in \IC{tot}
is a preasheaf in \D{PSh}.

@@

We write \D{∙} for the empty context and \Ar{Γ} \D{,,} \Ar{A} for the
extension of the context \Ar{Γ} with the type \Ar{A}. We have
the usual variable, weakening and substitutution operations.
%\subsection{Operations on Contexts}
%\subsection{Substitution}

\subsection{Simple Types}

\subsection{Later}

\subsection{Clock Quantification}

\subsection{Fix}

\subsection{Inductive Types}

\section{The Interpretation}

>>>>

\usepackage{newunicodechar}
\usepackage{stmaryrd}

@@

\newunicodechar{⊤}{$\top$}
\newunicodechar{≡}{$\equiv$}
\newunicodechar{₁}{$_1$}
\newunicodechar{₂}{$_2$}
\newunicodechar{Γ}{$\Gamma$}
\newunicodechar{Δ}{$\Delta$}
\newunicodechar{Σ}{$\Sigma$}
\newunicodechar{α}{$\alpha$}
\newunicodechar{γ}{$\gamma$}
\newunicodechar{ε}{$\varepsilon$}
\newunicodechar{λ}{$\lambda$}
\newunicodechar{μ}{$\mu$}
\newunicodechar{κ}{$\kappa$}
\newunicodechar{π}{$\pi$}
\newunicodechar{⊞}{$\boxplus$}
\newunicodechar{⊠}{$\boxtimes$}
\newunicodechar{∁}{$\mathbb{C}$}
\newunicodechar{►}{$\blacktriangleright$}
\newunicodechar{▻}{$\vartriangleright$}
\newunicodechar{𝟙}{\textbf{1}}
\newunicodechar{∙}{$\cdot$}
\newunicodechar{∀}{$\forall$}
\newunicodechar{ℓ}{$\ell$}
\newunicodechar{∅}{$\varnothing$}
\newunicodechar{⟶}{$\rightarrow$}
\newunicodechar{□}{$\square$}
\newunicodechar{⇡}{$\uparrow$}
\newunicodechar{⊛}{$\circledast$}
\newunicodechar{⊎}{$\uplus$}
\newunicodechar{⟨}{$\langle$}
\newunicodechar{⟩}{$\rangle$}
\newunicodechar{∎}{$\blacksquare$}
\newunicodechar{⇒}{$\Rightarrow$}
\newunicodechar{⊕}{$\oplus$}
\newunicodechar{⊗}{$\otimes$}
\newunicodechar{∼}{$\sim$}
\newunicodechar{≈}{$\approx$}
\newunicodechar{⊔}{$\sqcup$}
\newunicodechar{⟦}{$\llbracket$}
\newunicodechar{⟧}{$\rrbracket$}
\newunicodechar{⊥}{$\bot$}
% Add more as you need them (shouldn't happen often).

@@

% New commands for Agda inline code
\newcommand{\D}{\AgdaDatatype}
\newcommand{\IC}{\AgdaInductiveConstructor}
\newcommand{\F}{\AgdaFunction}
\newcommand{\Ar}{\AgdaArgument}
\newcommand{\Fi}{\AgdaField}
\newcommand{\AgdaUnderscore}{\_}

@@

\section{Preliminaries}
\input{Prelude/Basics}
%% \input{Presheaves/Presheaves}
%% \input{Presheaves/Const}
%% \input{Presheaves/Terminal}
%% \input{Presheaves/Product}
%% \input{Presheaves/Sum}
%% \input{Presheaves/Exp}
%% \input{CloTT/Structure/Contexts}
%% \input{CloTT/Structure/Types}
%% \input{CloTT/Structure/Terms}
%% \input{CloTT/Structure/DefinitionalEquality}
%% \input{CloTT/Structure/ContextOperations}
%% \input{CloTT/Structure/Subst}
%% \input{CloTT/TypeFormers/UnitType}
%% \input{CloTT/TypeFormers/SumType}
%% \input{CloTT/TypeFormers/ProductType}
%% \input{CloTT/TypeFormers/FunctionType}
%% \input{CloTT/TypeFormers/ClockQuantification}
%% \input{CloTT/TypeFormers/Later}
%% \input{CloTT/TypeFormers/LaterType}
%% \input{CloTT/TypeFormers/WeakenClock}
%% \input{CloTT/TypeFormers/Fix}
%% \input{CloTT/TypeFormers/Force}

@@

\section{Deep Embedding}
\input{Prelude/Syntax}

\section{Presheaf Semantics}
\subsection{Presheaaves}
\input{Presheaves/Presheaves}

\input{Presheaves/Const}

\input{Presheaves/Terminal}

\input{Presheaves/Sum}

\input{Presheaves/Product}

\input{Presheaves/Exp}

\subsection{Kripke Semantics}
A context in \IC{set} is an element of \D{Set}. A context in \IC{tot}
is a preasheaf in \D{PSh}.

@@

We write \D{∙} for the empty context and \Ar{Γ} \D{,,} \Ar{A} for the
extension of the context \Ar{Γ} with the type \Ar{A}. We have
the usual variable, weakening and substitutution operations.

\input{CloTT/Structure/ContextOperations}
\input{CloTT/Structure/Subst}
%\subsection{Operations on Contexts}
%\subsection{Substitution}

\section{Modelling Guarded Recursion}
\subsection{Later}
\input{CloTT/TypeFormers/Later}
\input{CloTT/TypeFormers/LaterType}
\input{CloTT/TypeFormers/Fix}

\subsection{Clock Quantification}
\input{CloTT/TypeFormers/ClockQuantification}
\input{CloTT/TypeFormers/ClockQuantificationType}

\subsection{Inductive Types}
\input{CloTT/TypeFormers/Mu}

\section{The Interpretation}
\input{GuardedTT}
